An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-27 VLDB2026/main.tex
Update main.tex

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.2cm}
		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. 2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries. In real-world applications, an object typically involves multiple attributes. For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
	3) It does not evaluate algorithm performance under different attribute distributions. However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.

@@

		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{0.2cm}
		\caption{Graph index and IVF index}

@@

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

	\begin{figure*}
		\centering
		%        \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		%    \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

		% 第一行：单独一张大图
		\begin{subfigure}{\textwidth}
			\centering
			%        \setlength{\abovecaptionskip}{0cm}
			%        \setlength{\belowcaptionskip}{0cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms optimized for low AS levels.}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.66\textwidth} % 2/3 宽度
			\centering
			%        \setlength{\abovecaptionskip}{0cm}
			%        \setlength{\belowcaptionskip}{0cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS levels.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hfill % 增加水平间距
		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
			\centering
			%        \setlength{\abovecaptionskip}{0cm}
			%        \setlength{\belowcaptionskip}{0cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS level.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		%    \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.4cm}
		\caption{Different AS under the same algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		%    \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

	\begin{figure*}[htbp]
		\centering
		%  \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		%    \setlength{\abovecaptionskip}{0cm}
		%    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

>>>>

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. 2) It \textcolor{yellow}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries. In real-world applications, an object typically involves multiple attributes.\textcolor{yellow}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
	3) It does not evaluate algorithm performance under different attribute distributions. However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.

@@

		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.02cm}
		\caption{Graph index and IVF index}

@@

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

	\begin{figure*}
		\centering
		        \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

		% 第一行：单独一张大图
		\begin{subfigure}{\textwidth}
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms optimized for low AS levels.}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.66\textwidth} % 2/3 宽度
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS levels.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hfill % 增加水平间距
		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS level.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		   \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\caption{Different AS under the same algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.02cm}
		\setlength{\belowcaptionskip}{0.02cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

	\begin{figure*}[htbp]
		\centering
		  \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}
